### 2012-09-29 doc/prelim/document/chapters/introduction/introduction.tex
finished motiviation

We discuss in this chapter our motivation for developing these Monte
Carlo solvers by providing background on the current state of solver
techniques for multiphysics problems and the hardware that they
leverage. In addition, multiphysics problems of interest to the
nuclear engineering community are provided to further motivate this
work. We then provide a formal presentation of the multiphysics system
and the problems that arise from it.

@@

>>>>

We discuss in this chapter our motivation for developing these Monte
Carlo solvers by providing multiphysics problems of interest to the
nuclear engineering community. In addition, background on the current
state of solver techniques for multiphysics problems and the hardware
that they leverage is provided to further motivate this work. We then
provide a formal presentation of the multiphysics system and the
problems that arise from it.

@@

The computational resources required to solve such problems are
tremendous. Recent work in modeling the coupled fluid flow and solid
model heat and mass transfer component of the departure from nucleate
boiling model above was performed as part of analysis of the
Department of Energy's Consortium for Advanced Simulation of Light
Water Reactors (CASL) modeling and simulation hub using the Drekar
multiphysics code \citep{pawlowski_drekar_2012}. Using Drekar,
multiphysics simulations have been performed with fully consistent
methods for the solution of nonlinear systems using meshes of
$O(\sn{1}{9})$ elements leveraging $O(100,000)$ cores on leadership
class machines. If we aim to advance multiphysics solution techniques,
then we are motivated to tackle the solution of complex and general
nonlinear problems exploiting leadership class levels of parallelism.
